Data Dashboard

### 2020-07-21 analysis/05_market_simulator.Rmd
Working on getting simulator to work

```{r load data}
charity_voluntarism <- readRDS(here('analysis', 'output', 'posterior_draws', 'charity_voluntarism.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))

@@

beta <- as.data.frame(matrix(rep(0), nrow = 13))
beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")

@@

```{r plot}
renderPlotly({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_noncentered[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_noncentered[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_noncentered[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_noncentered[,2])),2)
  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

@@

  ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Type)) +
             geom_col() +
             labs(x="") + 
             #scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48", "Oxfam" = "#006633", "Red Cross" = "#660000"))+
             theme(legend.position = "none") +
             facet_wrap(~Type)
    )
})
```

>>>>

```{r load data}

### Commented out the beta's we don't need right now. We only need the one that contains all the factors.

charity_voluntarism <- readRDS(here('analysis', 'output', 'posterior_draws', 'charity_voluntarism.rds')) %>%
  group_by(i) %>%
  summarize(theta_mean = mean(Theta))

@@

##### Updated the beta's to be just the betas from the public_political_social_chartiy_demo Thetas

beta <- public_political_social_charity_demo

beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")

@@

```{r plot}
renderPlotly({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_noncentered[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_noncentered[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_noncentered[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_noncentered[,2])),2)

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

@@

  ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Type)) +
             geom_col() +
             labs(x="") + 
             scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48", "Oxfam" = "#006633", "Red Cross" = "#660000"))+
             theme(legend.position = "none") +
             facet_wrap(~Type)
    )
})
```
